Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
swap rows in coln
fixed grlex order in noneffective genus 0

\ssec{Saturation}
\label{ssec:g_0_saturation} \todo{Define saturation}
Here we compute saturation numbers. That is, given a list of
ramification orders, with $g = 0,\delta = 0$ understood, we have
the following saturations of the canonical divisor, as defined in 7.
2 of VZB \cite{vzb:stacky}. Exceptional cases are listed first
and generic cases follow.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_3 \prec 
		y_4 \prec y_5$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

>>>>

\ssec{Saturation}
\label{ssec:g_0_saturation} \todo{Define saturation}
Here we compute saturation numbers. That is, given a list of
ramification orders, with $g = 0,\delta = 0$ understood, we have
the following saturations of the canonical divisor, as defined in 7.
2 of Voight and Zureick-Brown \cite{vzb:stacky}. Exceptional cases are listed first
and generic cases follow.

@@

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}
